## R code for analysis of the Ban Rai Rockshelter faunal data.

Cyler Conrad, Department of Anthropology, University of New Mexico, cylerc@unm.edu

This document contain R code to reproduce the plots and statistical analysis presented in: 

> Wattanapituksakul, A., Shoocongdej, R., and Conrad, C.. in review. Preservation of Mammalian Teeth and Bones Influences Terminal Pleistocene to Middle Holocene Hunter-Gatherer Subsistence at Ban Rai Rockshelter, Northwest Thailand. Quaternary.

*Please note that final script with corrected figure numbers and notation will be provided after peer review*

Details of the computational environment and software dependencies are listed at the end of this document. 

```{r setup, include=FALSE}
# set the base directory for knitr to the directory above this one
# install.packages(c("knitr", "car", "ggplot2", "reshape2", "plyr", "dplyr", "viridis, "ggpubr"))
library(knitr)
opts_knit$set(root.dir = '../', progress = FALSE)
```

```{r load_libraries, message = FALSE, warning = FALSE}
# see the output of sessionInfo() at the bottom for package version numbers
library(car)
library(ggplot2)
library(reshape2)
library(plyr)
library(dplyr)
library(viridis)
library(ggpubr)
```

```{r Load data}
rel<-read.csv("data/All_NISPNTAXA.csv")
layer1rev1<-read.csv("data/Area1Layer_rev1.csv")
layer1rev1mni<-read.csv("data/Area1Layer_rev1mni.csv")
layer2rev1<-read.csv("data/Area2Layer_rev1.csv")
layer2rev1mni<-read.csv("data/Area2Layer_rev1mni.csv")
layer3rev1<-read.csv("data/Area3Layer_rev1.csv")
fig5<-read.csv("data/fig5.csv")
fig6<-read.csv("data/fig6.csv")
btrev<-read.csv("data/Area3_btrev.csv")
```

```{r Relationship between NISP/MNI and NTAXA}
NISP<-ggplot(rel, aes(NISP, NTAXA)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm") +
  ggtitle("") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15),
        legend.text = element_text(size=15),
        legend.title = element_text(size=15))

MNI<-ggplot(rel, aes(MNI, NTAXA)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm") +
  ggtitle("") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15),
        legend.text = element_text(size=15),
        legend.title = element_text(size=15))
figure3 <- ggarrange(NISP, MNI,
                     labels = c("A", "B"),
                     nrow = 2)
figure3
ggexport(figure3, width = 1000, height = 1000, filename = "Relationships.png", res=200)

#Statistical Analysis
ggexport(figure3, width = 1000, height = 1000, filename = "Relationships.png", res=200)
nispntaxa<- lm(rel$NISP ~ rel$NTAXA)
summary(nispntaxa)
mnintaxa<- lm(rel$MNI ~ rel$NTAXA)
summary(mnintaxa)

nispntaxa.1<- lm(rel_rev$NISP ~ rel_rev$NTAXA)
summary(nispntaxa.1)
mnintaxa.1<- lm(rel_rev$MNI ~ rel_rev$NTAXA)
summary(mnintaxa.1)

#Without Area 3
rel<-read.csv("All_NISPNTAXA.csv")
rel
rel_rev <- rel[2:6, ]

NISP2<-ggplot(rel_rev, aes(NISP, NTAXA)) +
  geom_point(size = 3) +
  geom_smooth(method = "glm") +
  ggtitle("") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15),
        legend.text = element_text(size=15),
        legend.title = element_text(size=15))
MNI2<-ggplot(rel_rev, aes(MNI, NTAXA)) +
  geom_point(size = 3) +
  geom_smooth(method = "glm") +
  ggtitle("") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15),
        legend.text = element_text(size=15),
        legend.title = element_text(size=15))

figure4 <- ggarrange(NISP2, MNI2,
                     labels = c("A", "B"),
                     nrow = 2)
figure4
ggexport(figure4, width = 1000, height = 1000, filename = "Relationships_woutA3.png", res=200)
rel_rev
```

```{r Area 1 comparisons}
layer1rev1<-read.csv("Area1Layer_rev1.csv")
layer1rev1
S1E4 <- layer1rev1[1:20, ]
S2E12 <- layer1rev1[21:44, ]

A1_1 <-ggplot(S1E4, aes(Layer, NISP, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 1-Unit S1E4: NISP") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,22)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)
#ggsave("Area1S1E4_PerLayer.tiff", width = 11, height = 8.5, units = "in")

A1_2 <-ggplot(S2E12, aes(Layer, NISP, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 1-Unit S2E12: NISP") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,22)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)
#ggsave("Area1S2E12_PerLayer.tiff", width = 11, height = 8.5, units = "in")

figure1 <- ggarrange(A1_1, A1_2,
                    labels = c("A", "B"),
                    nrow = 2)
figure1
#ggexport(figure1, width = 1000, height = 1000, filename = "Area1.png", res=200)

#MNI
layer1rev1mni<-read.csv("Area1Layer_rev1mni.csv")
layer1rev1mni
S1E4mni <- layer1rev1mni[1:20, ]
S2E12mni <- layer1rev1mni[21:44, ]

A1_1mni <-ggplot(S1E4mni, aes(Layer, MNI, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 1-Unit S1E4: MNI") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)
A1_1mni
#ggsave("Area1S1E4_PerLayer.tiff", width = 11, height = 8.5, units = "in")

A1_2mni <-ggplot(S2E12mni, aes(Layer, MNI, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 1-Unit S2E12: MNI") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)
A1_2mni
#ggsave("Area1S2E12_PerLayer.tiff", width = 11, height = 8.5, units = "in")

figure8_rev <- ggarrange(A1_1, A1_2,A1_1mni, A1_2mni,
                     labels = c("A", "B", "C", "D"),
                     nrow = 2, ncol=2)

figure8_rev
#ggexport(figure8_rev, width = 2000, height = 2000, filename = "Area1_rev.png", res=200)

```

```{r Area 2 comparisons}
layer2rev1<-read.csv("Area2Layer_rev1.csv")
layer2rev1
S1E6 <- layer2rev1[1:16, ]
S2E14Baulk <- layer2rev1[17:28, ]
S2E14 <- layer2rev1[29:44, ]

A2_1<-ggplot(S1E6, aes(Layer, NISP, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 2-Unit S1E6: NISP") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,31)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)

A2_2<-ggplot(S2E14Baulk, aes(Layer, NISP, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 2-Unit S1E14 Baulk: NISP") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,31)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)

A2_3<-ggplot(S2E14, aes(Layer, NISP, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 2-Unit S2E14: NISP") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,31)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)

#MNI
layer2rev1mni<-read.csv("Area2Layer_rev1mni.csv")
layer2rev1mni
S1E6mni <- layer2rev1mni[1:16, ]
S2E14Baulkmni <- layer2rev1mni[17:28, ]
S2E14mni <- layer2rev1mni[29:44, ]

A2_1mni<-ggplot(S1E6mni, aes(Layer, MNI, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 2-Unit S1E6: MNI") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)

A2_2mni<-ggplot(S2E14Baulkmni, aes(Layer, MNI, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 2-Unit S2E14 Baulk: MNI") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)

A2_3mni<-ggplot(S2E14mni, aes(Layer, MNI, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("Area 2-Unit S2E14: MNI") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)

figure9_rev <- ggarrange(A2_1, A2_2, A2_3,
                         A2_1mni, A2_2mni, A2_3mni,
                     labels = c("A", "B", "C",
                                "D","E","F"),
                     nrow = 3, ncol=3)

figure9_rev
#ggexport(figure9_rev, width = 3000, height = 2000, filename = "Area2_rev.png", res=200)
```

```{r Area 3 comparisons}
N5_1<-ggplot(layer3rev1, aes(Layer, NISP, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  #ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)
ggsave("Area3_PerLayer.tiff", width = 11, height = 8.5, units = "in")


#MNI
layer3rev1mni<-read.csv("Area3Layer_rev1mni.csv")
layer3rev1mni

N5_2<-ggplot(layer3rev1mni, aes(Layer, MNI, color=Taxon, group=Taxon)) +
  geom_point(size=3) +
  #geom_smooth(method = "glm") +
  ggtitle("") +
  geom_line(linetype="dashed") +
  #xlim(0,75)+
  #ylim(0,10)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))+
  scale_color_hue(l=50, c=40)
ggsave("Area3_PerLayer_MNI.tiff", width = 11, height = 8.5, units = "in")


figure11_rev <- ggarrange(N5_1, N5_2,
                          labels = c("A", "B"),
                          nrow = 2)

figure11_rev
#ggexport(figure11_rev, width = 1000, height = 1000, filename = "Area3_rev.png", res=200)
```

```{r Area 3 bones and teeth}
ggplot(btrev, aes(Layer, NISP, fill=Type)) +
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.75)+
  geom_text(aes(label = NISP), fontface = "bold", vjust = 1.5,
            position = position_dodge(.9), size = 4) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15),
        legend.key.size = unit(1, 'cm'),
        legend.key.height = unit(1.5, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.title = element_text(size=20), 
        legend.text = element_text(size=15))+
  scale_fill_manual("Type", values = c("Bone" = "brown", "Tooth" = "gray"))
#ggsave("Area3_bt.tiff", width = 11, height = 8.5, units = "in")
```

```{r Abundance and NTAXA comparisons}
ggplot(fig5, aes(fill=Type, y=Abundance, x=Area)) + 
  geom_bar(position="stack", stat="identity") +
  scale_fill_viridis(discrete = T) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))
ggsave("All_Abundance.tiff", width = 5, height = 7, units = "in")

ggplot(fig6, aes(y=NTAXA, x=Area)) + 
  geom_bar(position="stack", stat="identity") +
  scale_fill_viridis(discrete = T) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        strip.background = element_rect(colour="white", fill="white"),
        strip.text.x = element_text(colour = "black", size = 15),
        axis.text.x = element_text(vjust=0.5, color="black", size=15),
        axis.text.y = element_text(vjust=0.5, color="black", size=15), 
        axis.title.y = element_text(vjust=1.0, color="black", size=15),
        axis.title.x = element_text(vjust=0.1, color="black", size=15),
        plot.title = element_text(hjust = 0.5, size=15))
ggsave("All_NTAXA.tiff", width = 5, height = 6, units = "in")
```

```{r session_info}
# Computational environment and software dependencies for this analysis.
sessionInfo()
```

MIT License

Copyright (c) 2021 Cyler Conrad

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.